% Tamaño de papel y fuente
\documentclass[a4paper, 12pt]{article}

% Márgenes
\usepackage[left=2cm, right=2cm, top=2cm, bottom=2cm]{geometry}

% Idioma
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}

% Fonts
\usepackage[T1]{fontenc}
% \usepackage[semibold]{ebgaramond}
% \renewcommand*\rmdefault{ppl}
\usepackage[scaled=1.09]{crimson}

% Interlineado
\usepackage{setspace}
\setstretch{1.15}

\usepackage{color}

\usepackage{array, xcolor, lipsum, bibentry, enumitem, etaremune}
\usepackage{color}
	\definecolor{dark_blue}{rgb}{0.2, 0.0, .7}
	\definecolor{some_blue}{HTML}{3b4a78}
\usepackage[colorlinks = TRUE, allcolors = some_blue]{hyperref}

% Tablas y gráficos
\usepackage[]{caption}
\usepackage{booktabs, graphicx}
\usepackage{pifont}
% \usepackage{fontawesome}

\usepackage[]{titlesec}
\titleformat*{\section}{\large\bfseries\flushleft}
\titleformat*{\subsection}{\normalsize\bf\flushleft}

\usepackage{lastpage}

\makeatletter
\renewcommand{\@evenfoot}%
{\small \hfil {\thepage}/\pageref{LastPage} \hfil}
\renewcommand{\@oddfoot}{\@evenfoot}
\makeatother

\usepackage{datetime}
\newdateformat{monthdate}{\monthname[\THEMONTH] \THEYEAR}

\renewcommand\labelitemi{\textbf{--}}

\begin{document}

% ---------------------------------------------------------
% BASIC HEADER + CONTACT INFO
% ---------------------------------------------------------

\begin{center}
{\bfseries\Large Francisco Villamil}
\end{center}

\vspace{0pt}

\noindent
\begin{minipage}[t]{0.47\textwidth}\small
\flushright
	Office 18.2.D15\\
	Universidad Carlos III de Madrid\\
	Madrid, 135 -- 28903 Getafe\\
\end{minipage}\hfill
\begin{minipage}[t]{0.47\textwidth}\small
	% \vfill
	\ding{37} \hspace{5pt} (+34) 91 624 8510\\
	\ding{41} \hspace{5pt} \href{mailto:francisco.villamil@uc3m.es}{francisco.villamil@uc3m.es}\\
	\ding{43} \hspace{5pt} \href{https://franvillamil.github.io}{https://franvillamil.github.io}\\
	% \ding{43} \hspace{5pt} \href{https://orcid.org/0000-0003-0523-5426}{orcid.org/0000-0003-0523-5426}
\end{minipage}


%---------------------------------------------------------------
% \vspace{-10pt}
\section*{Academic positions}

\begin{minipage}[t]{0.12\textwidth}
\textbf{2022--}
\end{minipage}\hfill\begin{minipage}[t]{0.88\textwidth}
Assistant Professor of Political Science\\
\textit{Department of Social Sciences, Universidad Carlos III de Madrid}\\\vspace{-8pt}
\end{minipage}\\
\begin{minipage}[t]{0.12\textwidth}
\textbf{2020--21}
\end{minipage}\hfill\begin{minipage}[t]{0.88\textwidth}
Junior Research Fellow\\
\textit{Carlos III-Juan March Institute, Universidad Carlos III de Madrid}\\\vspace{-8pt}
\end{minipage}\\
% \begin{minipage}[t]{0.1\textwidth}
% \textbf{2020--}
% \end{minipage}\hfill\begin{minipage}[t]{0.9\textwidth}
% Visiting Professor\\
% \textit{Department of Social Sciences, Universidad Carlos III de Madrid}
% \end{minipage}\\

%---------------------------------------------------------------
\vspace{-10pt}
\subsection*{Other}

% \noindent
\begin{minipage}[t]{0.82\textwidth}
  Visiting Scholar, \textit{Institute of Social Sciences}, Lisbon\vspace{2pt}\\
  Visiting Scholar, \textit{Carlos III-Juan March Institute}, Madrid\vspace{2pt}\\
	Visiting Researcher, \textit{Georgetown University}, Washington DC
\end{minipage}
\begin{minipage}[t]{0.18\textwidth}
  \flushright
  \setstretch{0.8}
	\textbf{2023}\\\vspace{7pt}
  \textbf{2019}\\\vspace{7pt}
	\textbf{2018--2019}
\end{minipage}

%---------------------------------------------------------------
\vspace{-0pt}
\section*{Education}

\begin{minipage}[t]{0.1\textwidth}
  \flushleft
	\textbf{2020}
\end{minipage}
\begin{minipage}[t]{0.9\textwidth}
  PhD Political Science, \textit{ETH Zurich}
	\vspace{-5pt}
	\begin{itemize}[leftmargin=18pt]\small
		\renewcommand\labelitemi{{\boldmath$\cdot$}}
	  \item \href{https://www.cepc.gob.es/premio-juan-linz}{Juan Linz Prize} to the Best Doctoral Dissertation in Political Science (CEPC, Spain)
	\end{itemize}
\end{minipage}

\vspace{10pt}

\noindent
\begin{minipage}[t]{0.1\textwidth}
  \flushleft
	\textbf{2016}
\end{minipage}
\begin{minipage}[t]{0.9\textwidth}
  MA Comparative and International Studies, \textit{ETH Zurich \& University of Zurich}
\end{minipage}

% \vspace{-10pt}

\noindent
\begin{minipage}[t]{0.1\textwidth}
  \flushleft
	\textbf{2014}
\end{minipage}
\begin{minipage}[t]{0.9\textwidth}
  BA Sociology, \textit{Universidad de Salamanca}
\end{minipage}

%---------------------------------------------------------------
\section*{Publications}

\subsection*{Peer-reviewed articles}

\begin{etaremune}[leftmargin=12pt, itemsep=0pt]
\item \textbf{Villamil, Francisco}, Stuart Turnbull-Dugarte, and José Rama (2024) \href{https://doi.org/10.1086/727598}{Rally 'round the barrack: Far-right support and the military.} \textit{The Journal of Politics}, forthcoming.
% \begin{itemize}[noitemsep,topsep=-10pt]
% 	\renewcommand\labelitemi{{\boldmath$\cdot$}}
%   \item {\small Media/outreach: \href{https://www.infolibre.es/politica/triunfo-vox-cuarteles-estudio-acredita-expansion-extrema-derecha-ejercito_1_1560872.html}{infoLibre}, \href{https://www.eldiario.es/piedrasdepapel/ejercito-extrema-derecha_132_10493272.html}{elDiario.es}}
% \end{itemize}
\item Balcells, Laia, Juan F Tellez, and \textbf{Francisco Villamil} (2024) \href{https://doi.org/10.1086/726939}{The wars of others: The effect of the Russian invasion of Ukraine on Spanish nationalism.} \textit{The Journal of Politics} 86(1): 352--357.
% \begin{itemize}[noitemsep,topsep=-10pt]
% 	\renewcommand\labelitemi{{\boldmath$\cdot$}}
%   \item {\small Media/outreach: \href{https://jop.blogs.uni-hamburg.de/the-impact-of-distant-wars-on-nationalism-lessons-from-spain/}{The JOP Blog}}, \href{https://www.eldiario.es/piedrasdepapel/guerras-afectan-politicamente_132_10640558.html}{elDiario.es}
% \end{itemize}
\item \textbf{Villamil, Francisco} (2023) \href{https://doi.org/10.1017/S1755773923000097}{Civilian victimization and ethnic attitudes in Africa.}\\\textit{European Political Science Review} 15(4): 617--627.
\item \textbf{Villamil, Francisco} (2022) \href{https://journals.sagepub.com/doi/full/10.1177/07388942211066539}{Violence, co-optation, and postwar voting in Guatemala.}\\\textit{Conflict Management and Peace Science} 39(6): 731--754.
% \begin{itemize}[noitemsep,topsep=-10pt]
% 	\renewcommand\labelitemi{{\boldmath$\cdot$}}
%   \item {\small Media/outreach: \href{https://www.civilwarpaths.org/2023/10/06/how-political-actors-influence-war-legacies/}{Civil War Paths Blog}}
% \end{itemize}
\item \textbf{Villamil, Francisco} and Laia Balcells (2021) \href{https://journals.sagepub.com/doi/full/10.1177/20531680211058550}{Do TJ policies cause backlash? Evidence from street name changes in Spain.} \textit{Research \& Politics} 8(4).
	% \begin{itemize}[noitemsep,topsep=-10pt]
	% 	\renewcommand\labelitemi{{\boldmath$\cdot$}}
	%   \item {\small Media/outreach: \href{https://www.eldiario.es/piedrasdepapel/justicia-transicional-memoria-historica_132_8453155.html}{elDiario.es}}
	% \end{itemize}
\item \textbf{Villamil, Francisco} (2021) \href{https://doi.org/10.1177/0022343320912816}{Mobilizing memories: The social conditions of the long-term impact of victimization.} \textit{Journal of Peace Research} 58(3): 399--416.
\item Balcells, Laia and \textbf{Francisco Villamil} (2020) \href{https://doi.org/10.1080/13537113.2020.1795451}{The double logic of internal purges: Evidence from Francoist Spain.} \textit{Nationalism and Ethnic Politics} 26(3): 260--278.
\item Cederman, Lars-Erik, Simon Hug, Livia Schubiger, and \textbf{Francisco Villamil} (2020) \href{https://doi.org/10.1177/0022002719898873}{Civilian victimization and ethnic civil war.} \textit{Journal of Conflict Resolution} 64(7--8): 1199--1225.
\end{etaremune}

\subsection*{Book chapters}

\begin{etaremune}[leftmargin=12pt, itemsep=0pt]
\item \textbf{Villamil, Francisco} (2023) Civil Wars. In: \href{https://www.e-elgar.com/shop/gbp/elgar-encyclopedia-of-political-sociology-9781803921228.html}{\textit{Encyclopedia of Political Sociology}}, edited by Maria T. Grasso and Marco Giugni. Cheltenham: Edward Elgar, 56--58. % ISBN: 978-1-80392-122-8
\item Rama, José, Stuart J. Turnbull-Dugarte and \textbf{Francisco Villamil} (2022) Descomponiendo a la derecha radical europea: el perfil de sus votantes. In: \href{https://www.comares.com/libro/en-los-margenes-de-la-democracia-liberal_143816/}{\textit{En los márgenes de la democracia liberal: Populismo, nacionalismo y radicalismo ideológico en Europa}}, edited by Ángel Valencia and Belén Fernández-García. Granada: Comares, 239--258. % ISBN: 978-84-1369-480-1
\end{etaremune}

%---------------------------------------------------------------
\section*{Working papers}

\begin{itemize}[leftmargin=*, nolistsep]
\item The legacies of authoritarian repression on civil society (with Laia Balcells).\\\href{https://doi.org/10.35188/UNU-WIDER/2023/309-3}{WIDER Working Paper 1/2023.} \textit{Revise and resubmit, CPS.}
\item Mobilization capacity and violence against local leaders: Anticlerical violence during the Spanish Civil War (with P. Aguilar, F. de la Cuesta, and I. Sánchez-Cuenca). \textit{Revise and resubmit, CPS.}
\item Measurement validity in historical conflict data: Comparing datasets from Spain.
\end{itemize}

%---------------------------------------------------------------
\section*{Research in progress}

\begin{itemize}[leftmargin=*, nolistsep]
\item Mobilizing memories: How violence leaves long-term legacies. (Book project.)
\item Past conflict, media, and polarization in Spain (with Laia Balcells and Juan F. Tellez).
\end{itemize}

%---------------------------------------------------------------
\section*{Teaching \& Supervision}

% \begin{minipage}[t]{0.1\textwidth}
% \textbf{yyyy}
% \end{minipage}\hfill\begin{minipage}[t]{0.9\textwidth}
% xxxx
% \end{minipage}\vspace{-5pt}\\

\subsection*{Graduate}

\noindent
\href{https://raw.githack.com/franvillamil/syllabi/master/current/syllabus_IR.pdf}{International Relations}\hfill\textbf{2022--2023}\\
{\small MA in Social Sciences, Carlos III-Juan March Institute}\\
{\small Evaluation: 5/5 (2023); 4.43/5 (2022)}
\vspace{10pt}

\noindent
\href{https://github.com/franvillamil/syllabi/blob/master/current/syllabus_research_design.pdf}{Research Design}\hfill\textbf{Fall 2022}\\
{\small MA in Computational Social Science, Universidad Carlos III de Madrid}\\
{\small Evaluation: 4.06/5 (2023); 3.5/5 (2022)}

% \vspace{-10pt}
\subsection*{Undergraduate}

\noindent
\href{https://github.com/franvillamil/syllabi/blob/master/current/syllabus_war_peace_political_violence.pdf}{War, peace, and political violence}\hfill\textbf{2020--2022}\\
{\small Undergraduate course, Universidad Carlos III de Madrid}\\
{\small Evaluation: 4.25/5 (2023); 4.72/5 (2022); 4.74/5 (2021); 4.21/5 (2020)}
\vspace{10pt}

\noindent
Multidisciplinary seminar on International Studies\hfill\textbf{2020--2021}\\
{\small Undergraduate course, Universidad Carlos III de Madrid}\\
{\small Evaluation: 4.5/5 (2021); 4.67/5 (2021); 4.63/5 (2020); 4.24/5 (2020)}
\vspace{10pt}

\noindent
Security, peace, and conflict resolution\hfill\textbf{Fall 2020}\\
{\small Undergraduate course, Universidad Carlos III de Madrid}\\
{\small Evaluation: 4.71/5 (2020)}

%---------------------------------------------------------------
\section*{Supervision}

\begin{itemize}[leftmargin=*, nolistsep]
	\item Nadal Perales (PhD co-supervisor, UC3M, 2022--).
\end{itemize}

\subsection*{Master theses}

2023: Kaan Bakmaz, Alejandro Aisa, Carolina Cornejo, Artem Urlapov;
2022: Mario Pirez;
2021: Javier Terraza.

%---------------------------------------------------------------
\section*{Data \& Software}

\begin{itemize}[leftmargin=*, nolistsep]
  \item \href{https://github.com/franvillamil/muniSpain}{muniSpain}: R package for historical municipality-level analyses in Spain
	\item Coder coordinator, ACD2EPR Version 2018 (\href{https://icr.ethz.ch/data/epr/acd2epr/ACD2EPR-2018_Codebook.pdf}{codebook,} \href{https://icr.ethz.ch/data/epr/acd2epr/}{website})
	\item Coder coordinator and coder, EOSV dataset (\href{https://snis.ch/project/civilian-victimization-conflict-escalation/}{website}), 2016--2017
\end{itemize}

%---------------------------------------------------------------
\section*{Talks}

\subsection*{Conferences}

\noindent
APSA Annual Meeting\hfill\textbf{2017, 2018, 2022}\\
EPSA Annual Conference\hfill\textbf{2017}\\
NEPS Jan Tinbergen Peace Science Conference\hfill\textbf{2018, 2019, 2021--2023}\\
CES International Conference of Europeanists\hfill\textbf{2022}\\\vspace{15pt}

% \hfill{\footnotesize ($\star$ = discussant, $\dagger$ = chair)}

\vspace{-20pt}

\subsection*{Workshops, seminars \& invited talks}

\textbf{2023:} Institute of Social Sciences, Lisbon; STNAMES Lab Workshop, Universidad Pablo de Olavide, Seville. \textbf{2022:} Institutional legacies of violent conflict workshop, UNU-WIDER, Helsinki. \textbf{2021:} Trust \& Governance Workshop, online. \textbf{2020:} Carlos III--Juan March Institute, Madrid.

%---------------------------------------------------------------
\section*{Awards}

% \begin{minipage}[t]{0.1\textwidth}
% \textbf{yyyy}
% \end{minipage}\hfill\begin{minipage}[t]{0.9\textwidth}
% xxxx
% \end{minipage}\\

\begin{minipage}[t]{0.1\textwidth}
\textbf{2021}
\end{minipage}\hfill\begin{minipage}[t]{0.9\textwidth}
Juan Linz Price to the Best Doctoral Dissertation in Political Science,\\\textit{Centro de Estudios Políticos y Constitucionales (Spanish Ministry of the Presidency)}\\\vspace{-8pt}
\end{minipage}
\begin{minipage}[t]{0.1\textwidth}
\textbf{2018}
\end{minipage}\hfill\begin{minipage}[t]{0.9\textwidth}
Swiss Academy of Humanities and Social Sciences (SAGW) travel grant
\end{minipage}\\
\begin{minipage}[t]{0.1\textwidth}
\textbf{2014}
\end{minipage}\hfill\begin{minipage}[t]{0.9\textwidth}
Best academic record in undergraduate studies, {\it Universidad de Salamanca}
\end{minipage}\\
\begin{minipage}[t]{0.1\textwidth}
\textbf{2013}
\end{minipage}\hfill\begin{minipage}[t]{0.9\textwidth}
Undergraduate research assistant fellowship, {\it Spanish Ministry of Education}
\end{minipage}\\

%---------------------------------------------------------------
\section*{Research grants}

\subsection*{As PI}

\begin{itemize}[leftmargin=12pt, itemsep=0pt]
  \item Local-level dynamics and consequences of Transitional Justice: Mass grave exhumations in Spain. Spanish Ministry of the Presidency, 9,960 €, 2023--2024. % 205-MD-2023
\end{itemize}

\subsection*{As participant}

\begin{itemize}[leftmargin=12pt, itemsep=0pt]
	\item How does nationalist identity shape political attitudes toward redistribution and political violence? Evidence from sporting events. Spanish Ministry of Science and Innovation, 150,000 € (PI: Nikitas Konstantinidis), 2023--2026. % PID2022-139998NB-I00
	\item Determinants of violence during the Spanish Civil War and its long-term consequences. Spanish Ministry of the Presidency, 10,000 € (PI: Paloma Aguilar), 2022--2023. % 102-MD-2022
	\item Determinants of violence during the Spanish Civil War and its long-term consequences. Spanish Ministry of the Presidency, 10,000 € (PI: Paloma Aguilar), 2021--2022. % 191-MD-2021
	\item Institutional legacies of violent conflict. UNU-WIDER, 10,000 \$ (PI: Laia Balcells), 2021.
\end{itemize}


%---------------------------------------------------------------
\section*{Skills}

Software: R, Stata, Python (beginner), MySQL (beginner), QGIS\\
Languages: English, Spanish (native), Portuguese (intermediate), German (basic)

%---------------------------------------------------------------
% \vspace{-10pt}
\section*{Service}

\subsection*{University}

\begin{itemize}[leftmargin=12pt, itemsep=0pt]
  \item Bachelor thesis coordinator, International Studies and Political Science, UC3M (2022--).
	\item Academic Committee, MA in Computational Social Social, UC3M (2022--).
	\item IC3JM Internal Seminar, coordinator (2021--2023).
\end{itemize}

\subsection*{Peer review}

American Political Science Review, The Journal of Politics, Nature Human Behaviour, British Journal of Political Science, Comparative Political Studies, Journal of Conflict Resolution, Journal of Peace Research, European Political Science Review, Political Behavior, Political Geography, Review of International Organizations, Civil Wars, Economics of Transition, Defence and Peace Economics, International Journal of Human Rights, Journal of Human Rights, Memory Studies, Social Movement Studies.


% %---------------------------------------------------------------
% \section*{References}
%
% \textit{Upon request.}

% \noindent
% \begin{minipage}[t]{0.28\textwidth}
% Lars-Erik Cederman\\\vspace{-10pt}
%
% Professor\\
% International Conflict\\Research,
% ETH Zürich\\
% +41 44 632 67 59\\
% {\small \url{lcederman@ethz.ch}}
% \end{minipage}
% \begin{minipage}[t]{0.35\textwidth}
% Laia Balcells\\\vspace{-10pt}
%
% Provost's Disting Assoc Prof\\
% Dept of Government,\\
% Georgetown University\\
% +1 (202) 687 3712\\
% {\small \url{laia.balcells@georgetown.edu}}
% \end{minipage}
% \begin{minipage}[t]{0.35\textwidth}
% Ignacio Sánchez-Cuenca\\\vspace{-10pt}
%
% Professor\\
% Carlos III-Juan March Institute,\\
% University Carlos III in Madrid\\
% +34 91 624 8505\\
% {\small \url{igsanche@clio.uc3m.es}}\\
% \end{minipage}

\vfill

\noindent
\flushright
{\small\it Updated \monthdate\today}

\end{document}
